---
title: "Deputy heads overview"
format:
  html:
    df-print: paged
    self-contained: true
    prefer-html: true
---

```{r}
#| echo: false
#| output: false
library(tidyverse)
library(DT)
```

```{r}
#| echo: false
#| output: false
#| cache: true
source("load/appointment-orders.R")
source("load/salary-orders.R")
```

Hello! We have, depending on the source (and assuming our standardizing worked properly!):

- `r appointments_classified %>% distinct(name_standardized) %>% pull() %>% length()` deputy heads, according to the appointment orders
- `r salary_revisions_classified %>% distinct(name_standardized) %>% pull() %>% length()` deputy heads, according to the salary orders

Here are names that are in the salary set, but not the appointments set:

```{r}
appointments_classified %>%
  count(name_standardized, name = "appointments") %>%
  full_join(
    salary_revisions_classified %>%
      count(name_standardized, name = "salary")) %>%
  mutate(in_both = ! is.na(appointments) & ! is.na(salary)) %>%
  arrange(name_standardized) %>%
  datatable()
```
